Binocular integration of chromatic and luminance signals

### 2024-03-31 manuscript.Rmd
Added autobuild files

processdata <- 1
# the processdata flag has three settings:
# 0: do no analysis, just produce the pdf of the manuscript
# 1: fit psychometric functions and plot graphs
# 2: do Stan modelling and simplex fitting (takes several hours, simplex sometimes gets stuck!)

@@

osfrepo <- '3vdga'

if (!file.exists('local/Experiment1.csv')){}
if (!file.exists('local/Experiment2.csv')){}
if (!file.exists('local/Experiment3.csv')){}
if (!file.exists('local/fundamentals.csv')){}
if (!file.exists('local/isosettings.csv')){}
if (!file.exists('local/phosphors.csv')){}

if (processdata < 1){
 if (!file.exists('local/thresholddata.RData')){}
 if (!file.exists('local/thresholddataDisc.RData')){}
 if (!file.exists('local/MCSdata.RData')){}
}

if (processdata < 2){
 if (!file.exists('local/simplexfits.RData')){}
 if (!file.exists('local/stanfit1.RData')){}
 if (!file.exists('local/stanfit2.RData')){}
 if (!file.exists('local/stanfit3.RData')){}
 if (!file.exists('local/stanfit4.RData')){}
}

if (!file.exists('references.bib')){}
if (!file.exists('journal-of-vision.csl')){}

@@

For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit). The best model fits are shown by the curves in Figures \@ref(fig:dipperfig) & \@ref(fig:discdata), and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB. Best fitting parameters are shown in the 'Simplex fits' section of Table \@ref(tab:parametertable). We note that in previous work, the weight of interocular suppression ($\omega$ in the model) is implicitly fixed at 1. Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (`r round(allp[4,6],digits=2)`) for our flickering discs. The exponent values (*p* and *q*) for the red/green gratings are rather different from those of the other conditions. In previous work [@Meese2006] the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper). The high value of *p* (`r round(allp[2,1], digits=2)`) is therefore likely to be compensating for the low value of *m* (`r round(allp[2,3], digits=2)`) at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].

>>>>

processdata <- 0
# the processdata flag has three settings:
# 0: do no analysis, just produce the pdf of the manuscript
# 1: fit psychometric functions and plot graphs
# 2: do Stan modelling and simplex fitting (takes several hours, simplex sometimes gets stuck!)

@@

osfrepo <- '3vdga'
osfproject <- osf_retrieve_node(osfrepo)
osffiles <- osf_ls_files(osfproject,n_max=300)

if (!file.exists('local/Experiment1.csv')){osf_download(osffiles[which(osffiles$name=='Experiment1.csv'),],'local/',progress=TRUE)}
if (!file.exists('local/Experiment2.csv')){osf_download(osffiles[which(osffiles$name=='Experiment2.csv'),],'local/',progress=TRUE)}
if (!file.exists('local/Experiment3.csv')){osf_download(osffiles[which(osffiles$name=='Experiment3.csv'),],'local/',progress=TRUE)}
if (!file.exists('local/fundamentals.csv')){osf_download(osffiles[which(osffiles$name=='fundamentals.csv'),],'local/',progress=TRUE)}
if (!file.exists('local/isosettings.csv')){osf_download(osffiles[which(osffiles$name=='isosettings.csv'),],'local/',progress=TRUE)}
if (!file.exists('local/phosphors.csv')){osf_download(osffiles[which(osffiles$name=='phosphors.csv'),],'local/',progress=TRUE)}

if (processdata < 1){
 if (!file.exists('local/thresholddata.RData')){osf_download(osffiles[which(osffiles$name=='thresholddata.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/thresholddataDisc.RData')){osf_download(osffiles[which(osffiles$name=='thresholddataDisc.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/MCSdata.RData')){osf_download(osffiles[which(osffiles$name=='MCSdata.RData'),],'local/',progress=TRUE)}
}

if (processdata < 2){
 if (!file.exists('local/simplexfits.RData')){osf_download(osffiles[which(osffiles$name=='simplexfits.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit1.RData')){osf_download(osffiles[which(osffiles$name=='stanfit1.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit2.RData')){osf_download(osffiles[which(osffiles$name=='stanfit2.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit3.RData')){osf_download(osffiles[which(osffiles$name=='stanfit3.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit4.RData')){osf_download(osffiles[which(osffiles$name=='stanfit4.RData'),],'local/',progress=TRUE)}
}

# if (!file.exists('references.bib')){}
# if (!file.exists('journal-of-vision.csl')){}

@@

For consistency with previous work, we initially performed least-squares fits of the two-stage model [@Meese2006] for each of the chromaticity experiments, and the flickering disc experiment (7 free parameters per fit). The best model fits are shown by the curves in Figures \@ref(fig:dipperfig) & \@ref(fig:discdata), and provide an excellent description of the data, with RMS errors between `r round(min(allrms),digits=2)` and `r round(max(allrms),digits=2)`dB. Best fitting parameters are shown in the 'Simplex fits' section of Table \@ref(tab:parametertable). We note that in previous work, the weight of interocular suppression ($\omega$ in the model) is implicitly fixed at 1. Here we allowed it to vary, but it still received a value of exactly 1 in all of our grating conditions, and slightly below 1 (`r round(allp[4,6],digits=2)`) for our flickering discs. The exponent values (*p* and *q*) for the red/green gratings are rather different from those of the other conditions. In previous work [@Meese2006] the second stage gain control nonlinearity (Equation 4) does typically have quite substantial exponent values, which balance the relatively mild nonlinearity at the first stage, and produce a compressive transducer that results in contrast masking (the handle of the dipper). The high value of *p* = `r round(allp[2,1], digits=2)` is therefore likely to be compensating for the low value of *m* = `r round(allp[2,3], digits=2)` at stage one, but may well represent the combination of several successive stages of nonlinearity, and perhaps also other phenomena such as uncertainty [@Pelli1985].
